---
title: "`r params$ticker` Decomposition Report"
output: html_document
params:
  ticker: "TICKER"
  # Price decomposition
  decomposition_data: NULL
  decomposition_metric_display_name: "NOPAT"
  decomposition_numerator: "price"
  decomposition_base_date: NULL
  # TSR decomposition
  tsr_decomposition_data: NULL
  # KPI per share (share count decomposition)
  share_count_decomposition_data: NULL
  kpi_metric_display_name: "NOPAT"
  # DuPont decomposition
  dupont_data: NULL
  dupont_numerator_name: "NOPAT"
  dupont_denominator_name: "Invested Capital"
  dupont_return_label: "ROIC"
  dupont_roa_label: "ROA"
  dupont_effect_label: "Capital Efficiency Effect"
  dupont_multiplier_label: "Assets / IC"
  dupont_title_suffix: "ROIC Decomposition"
  dupont_footnote: NULL
  # IC decomposition
  ic_decomposition_data: NULL
  # NOPAT decomposition
  nopat_decomposition_data: NULL
  nopat_metric_name: "NOPAT"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
set_ggplot_theme()
```

## Total Shareholder Return

```{r tsr-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$tsr_decomposition_data) && nrow(params$tsr_decomposition_data) > 0) {
  plot_tsr_decomposition(
    data = params$tsr_decomposition_data,
    ticker = params$ticker,
    base_date = params$decomposition_base_date
  )
}
```

## Per Share Growth

```{r share-count-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$share_count_decomposition_data) && nrow(params$share_count_decomposition_data) > 0) {
  plot_share_count_decomposition(
    data = params$share_count_decomposition_data,
    ticker = params$ticker,
    metric_name = params$kpi_metric_display_name,
    base_date = params$decomposition_base_date
  )
}
```

## `r params$dupont_title_suffix`

```{r dupont-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$dupont_data) && nrow(params$dupont_data) > 0) {
  plot_dupont_over_time(
    data = params$dupont_data,
    ticker = params$ticker,
    return_label = params$dupont_return_label,
    effect_label = params$dupont_effect_label,
    numerator_name = params$dupont_numerator_name,
    denominator_name = params$dupont_denominator_name,
    multiplier_label = params$dupont_multiplier_label,
    title_suffix = params$dupont_title_suffix,
    roa_label = params$dupont_roa_label
  )
}
```

## Invested Capital Decomposition

```{r ic-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$ic_decomposition_data) && nrow(params$ic_decomposition_data) > 0) {
  plot_ic_decomposition(
    data = params$ic_decomposition_data,
    ticker = params$ticker,
    base_date = params$decomposition_base_date
  )
}
```

## `r params$nopat_metric_name` Decomposition

```{r nopat-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$nopat_decomposition_data) && nrow(params$nopat_decomposition_data) > 0) {
  plot_nopat_decomposition(
    data = params$nopat_decomposition_data,
    ticker = params$ticker,
    metric_name = params$nopat_metric_name,
    base_date = params$decomposition_base_date
  )
}
```

---

## Methodology

### TSR Decomposition

The TSR (Total Shareholder Return) chart decomposes cumulative shareholder returns into market cap growth and the share count effect. TSR is measured as the cumulative percentage change in adjusted close price, which captures both price appreciation and dividend reinvestment. Market cap is calculated as adjusted close multiplied by shares outstanding, so changes in market cap reflect total value growth on a dividend-adjusted basis. The share count effect is the residual: TSR minus market cap growth. A positive share count effect indicates that buybacks have boosted per-share returns relative to total value growth; a negative effect indicates dilution from share issuances.

### Per Share Growth Decomposition

The per share growth chart decomposes cumulative growth in a metric per share into two additive components: total metric growth (the numerator effect) and the share count effect (the denominator effect). Total metric growth measures the cumulative percentage change in the aggregate metric (e.g., total NOPAT, which may include both organic growth and inorganic contributions such as M&A). The share count effect is calculated as the residual: per share growth minus total metric growth. This residual captures the full impact of share count changes on per share performance. Note that the share count effect will differ from the raw percentage change in shares because the impact of buybacks or dilution is magnified when the underlying metric is also growing. For example, a 20% reduction in shares applied to a metric that has grown 50% will produce a share count effect greater than 20%, since fewer shares are dividing a larger profit base.

### Invested Capital Decomposition

The invested capital decomposition chart shows cumulative change in invested capital (IC = Debt + Equity) broken down into four additive components. Net Income represents internal capital generation from operations (cumulative quarterly net income). Dividends represent capital returned to shareholders (shown as negative values). Debt Change represents the net change in borrowed capital (debt plus lease obligations) from the balance sheet. Equity Capital Activity is a residual component capturing the net effect of share buybacks, issuances, and other comprehensive income: it equals the actual change in equity minus cumulative net income minus cumulative dividends. For companies with significant buyback programs, this component will typically be negative, reflecting capital returned to shareholders beyond dividends. Unlike the other decompositions in this report, this analysis uses dollar amounts rather than percentages, providing a direct view of the magnitude of capital flows.

### NOPAT Decomposition

The NOPAT decomposition chart shows cumulative change in NOPAT (or another profitability metric) broken down into two additive components that explain the nature of earnings growth. Capital Deployment measures the NOPAT contribution from incremental capital invested since the base period, calculated as (IC_t - IC_0) × ROIC_t. This component captures how much of the earnings growth comes from deploying additional capital at current returns. ROIC Effect measures the change in NOPAT due to efficiency improvements or deterioration on the base capital, calculated as IC_0 × (ROIC_t - ROIC_0). A positive ROIC effect indicates the company is earning better returns on its original capital base; a negative effect indicates deteriorating returns. When Capital Deployment dominates, the company is scaling its business model. When ROIC Effect dominates, growth is coming from operational improvements. When both are positive, the company is both scaling and improving efficiency. When Capital Deployment is positive but ROIC Effect is negative, the company may be experiencing diminishing returns on new investments.

```{r appendix-dupont-header, results='asis'}
if (!is.null(params$dupont_footnote)) {
  cat("### DuPont Decomposition\n\n")
}
```

```{r appendix-dupont-notes, results='asis'}
if (!is.null(params$dupont_footnote)) {
  cat('<p style="color: #666666; font-size: 0.85em; text-align: left;">')
  cat(params$dupont_footnote)
  cat('</p>\n')
}
```
