---
title: "`r params$ticker` Fundamentals Report"
output: html_document
params:
  ticker: "TICKER"
  data: NULL
  per_share_revenue: NULL
  per_share_gross_profit: NULL
  per_share_ebit: NULL
  per_share_ebitda: NULL
  per_share_nopat: NULL
  per_share_fcf: NULL
  per_share_cfo: NULL
  per_share_bv: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
set_ggplot_theme()

prep_metric <- function(data, metric_col) {
  data %>%
    dplyr::select(fiscalDateEnding, value = dplyr::all_of(metric_col)) %>%
    dplyr::filter(!is.na(value))
}
```

## Financial Statements {.tabset}

### Income Statement {.tabset}

#### Revenue

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "revenue"), params$ticker, "Revenue (TTM)")
```

#### Cost of Revenue

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "cost_of_revenue"), params$ticker, "Cost of Revenue (TTM)")
```

#### Gross Profit

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "gross_profit"), params$ticker, "Gross Profit (TTM)")
```

#### SG&A

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "sga"), params$ticker, "SG&A (TTM)")
```

#### R&D

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "rd"), params$ticker, "R&D (TTM)")
```

#### Operating Expenses

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "operating_expenses"), params$ticker, "Operating Expenses (TTM)")
```

#### Operating Income

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "operating_income"), params$ticker, "Operating Income (TTM)")
```

#### EBIT

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "ebit"), params$ticker, "EBIT (TTM)")
```

#### EBITDA

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "ebitda"), params$ticker, "EBITDA (TTM)")
```

#### NOPAT

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "nopat"), params$ticker, "NOPAT (TTM)")
```

#### Interest Expense

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "interest_expense"), params$ticker, "Interest Expense (TTM)")
```

#### Income Before Tax

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "income_before_tax"), params$ticker, "Income Before Tax (TTM)")
```

#### Tax Expense

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "tax_expense"), params$ticker, "Tax Expense (TTM)")
```

#### Net Income

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "net_income"), params$ticker, "Net Income (TTM)")
```

#### D&A

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "depreciation_amortization"), params$ticker, "Depreciation & Amortization (TTM)")
```

### Cash Flow Statement {.tabset}

#### Operating Cash Flow

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "operating_cashflow"), params$ticker, "Operating Cash Flow (TTM)")
```

#### Free Cash Flow

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "fcf"), params$ticker, "Free Cash Flow (TTM)")
```

#### CapEx

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "capex"), params$ticker, "Capital Expenditures (TTM)")
```

#### Dividends

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "dividends"), params$ticker, "Dividends (TTM)")
```

#### Buybacks

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "buybacks"), params$ticker, "Share Buybacks (TTM)")
```

*Positive = share repurchases (capital returned to shareholders). Negative = share issuance (dilution).*

#### Total Capital Returned

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "total_capital_returned"), params$ticker, "Total Capital Returned (TTM)")
```

*Dividends + Share Buybacks*

#### Cash from Investing

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "cashflow_investing"), params$ticker, "Cash from Investing (TTM)")
```

#### Cash from Financing

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "cashflow_financing"), params$ticker, "Cash from Financing (TTM)")
```

### Balance Sheet {.tabset}

#### Total Assets

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "total_assets"), params$ticker, "Total Assets")
```

#### Current Assets

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "current_assets"), params$ticker, "Current Assets")
```

#### Non-Current Assets

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "non_current_assets"), params$ticker, "Non-Current Assets")
```

#### Cash

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "cash"), params$ticker, "Cash & Short-Term Investments")
```

#### Inventory

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "inventory"), params$ticker, "Inventory")
```

#### Receivables

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "receivables"), params$ticker, "Receivables")
```

#### PP&E

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "ppe"), params$ticker, "Property, Plant & Equipment")
```

#### Intangibles

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "intangibles"), params$ticker, "Intangible Assets")
```

#### Goodwill

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "goodwill"), params$ticker, "Goodwill")
```

#### Total Liabilities

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "total_liabilities"), params$ticker, "Total Liabilities")
```

#### Current Liabilities

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "current_liabilities"), params$ticker, "Current Liabilities")
```

#### Non-Current Liabilities

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "non_current_liabilities"), params$ticker, "Non-Current Liabilities")
```

#### Total Debt

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "total_debt"), params$ticker, "Total Debt")
```

#### Long-Term Debt

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "long_term_debt"), params$ticker, "Long-Term Debt")
```

#### Short-Term Debt

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "short_term_debt"), params$ticker, "Short-Term Debt")
```

#### Shareholder Equity

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "shareholder_equity"), params$ticker, "Shareholder Equity")
```

#### Retained Earnings

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "retained_earnings"), params$ticker, "Retained Earnings")
```

#### Shares Outstanding

```{r, fig.width=10, fig.height=6}
plot_fundamental_bar(prep_metric(params$data, "shares_outstanding"), params$ticker, "Shares Outstanding")
```

## Per-Share Growth {.tabset}

### Revenue

```{r per-share-revenue, fig.width=10, fig.height=6}
if (!is.null(params$per_share_revenue) && nrow(params$per_share_revenue) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_revenue,
    ticker = params$ticker,
    metric_name = "Revenue"
  )
}
```

### Gross Profit

```{r per-share-gross-profit, fig.width=10, fig.height=6}
if (!is.null(params$per_share_gross_profit) && nrow(params$per_share_gross_profit) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_gross_profit,
    ticker = params$ticker,
    metric_name = "Gross Profit"
  )
}
```

### EBIT

```{r per-share-ebit, fig.width=10, fig.height=6}
if (!is.null(params$per_share_ebit) && nrow(params$per_share_ebit) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_ebit,
    ticker = params$ticker,
    metric_name = "EBIT"
  )
}
```

### EBITDA

```{r per-share-ebitda, fig.width=10, fig.height=6}
if (!is.null(params$per_share_ebitda) && nrow(params$per_share_ebitda) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_ebitda,
    ticker = params$ticker,
    metric_name = "EBITDA"
  )
}
```

### NOPAT

```{r per-share-nopat, fig.width=10, fig.height=6}
if (!is.null(params$per_share_nopat) && nrow(params$per_share_nopat) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_nopat,
    ticker = params$ticker,
    metric_name = "NOPAT"
  )
}
```

### FCF

```{r per-share-fcf, fig.width=10, fig.height=6}
if (!is.null(params$per_share_fcf) && nrow(params$per_share_fcf) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_fcf,
    ticker = params$ticker,
    metric_name = "FCF"
  )
}
```

### Operating Cash Flow

```{r per-share-cfo, fig.width=10, fig.height=6}
if (!is.null(params$per_share_cfo) && nrow(params$per_share_cfo) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_cfo,
    ticker = params$ticker,
    metric_name = "Operating Cash Flow"
  )
}
```

### Book Value

```{r per-share-bv, fig.width=10, fig.height=6}
if (!is.null(params$per_share_bv) && nrow(params$per_share_bv) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_bv,
    ticker = params$ticker,
    metric_name = "Book Value"
  )
}
```
