---
title: "`r params$ticker` Fundamentals Report"
output: html_document
params:
  ticker: "TICKER"
  data: NULL
  tsr_data: NULL
  base_date: NULL
  drawdown_data: NULL
  per_share_revenue: NULL
  per_share_gross_profit: NULL
  per_share_ebit: NULL
  per_share_ebitda: NULL
  per_share_nopat: NULL
  per_share_fcf: NULL
  per_share_cfo: NULL
  per_share_bv: NULL
  roic_data: NULL
  roic_labels: NULL
  roe_data: NULL
  roe_labels: NULL
  kpi_data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
set_ggplot_theme()

prep_metric <- function(data, metric_col) {
  data %>%
    dplyr::select(fiscalDateEnding, value = dplyr::all_of(metric_col)) %>%
    dplyr::filter(!is.na(value))
}

safe_bar_plot <- function(data, metric_col, ticker, title) {
  prepped <- prep_metric(data, metric_col)
  if (nrow(prepped) > 0) {
    plot_fundamental_bar(prepped, ticker, title)
  }
}
```

## Price Charts {.tabset}

### TSR Decomposition

```{r tsr-decomposition, fig.width=10, fig.height=8}
if (!is.null(params$tsr_data) && nrow(params$tsr_data) > 0) {
  plot_tsr_decomposition(
    data = params$tsr_data,
    ticker = params$ticker,
    base_date = params$base_date
  )
}
```

### Drawdown

```{r drawdown-chart, fig.width=10, fig.height=6}
if (!is.null(params$drawdown_data) && nrow(params$drawdown_data) > 0) {
  plot_drawdown(
    data = params$drawdown_data,
    ticker = params$ticker,
    show_anomalies = FALSE
  )
}
```

## Financial Statements {.tabset}

### Income Statement {.tabset}

#### Revenue

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "revenue", params$ticker, "Revenue (TTM)")
```

#### Cost of Revenue

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "cost_of_revenue", params$ticker, "Cost of Revenue (TTM)")
```

#### Gross Profit

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "gross_profit", params$ticker, "Gross Profit (TTM)")
```

#### SG&A

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "sga", params$ticker, "SG&A (TTM)")
```

#### R&D

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "rd", params$ticker, "R&D (TTM)")
```

#### Operating Expenses

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "operating_expenses", params$ticker, "Operating Expenses (TTM)")
```

#### Operating Income

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "operating_income", params$ticker, "Operating Income (TTM)")
```

#### EBIT

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "ebit", params$ticker, "EBIT (TTM)")
```

#### EBITDA

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "ebitda", params$ticker, "EBITDA (TTM)")
```

#### NOPAT

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "nopat", params$ticker, "NOPAT (TTM)")
```

#### Interest Expense

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "interest_expense", params$ticker, "Interest Expense (TTM)")
```

#### Income Before Tax

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "income_before_tax", params$ticker, "Income Before Tax (TTM)")
```

#### Tax Expense

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "tax_expense", params$ticker, "Tax Expense (TTM)")
```

#### Net Income

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "net_income", params$ticker, "Net Income (TTM)")
```

#### D&A

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "depreciation_amortization", params$ticker, "Depreciation & Amortization (TTM)")
```

### Cash Flow Statement {.tabset}

#### Operating Cash Flow

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "operating_cashflow", params$ticker, "Operating Cash Flow (TTM)")
```

#### Free Cash Flow

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "fcf", params$ticker, "Free Cash Flow (TTM)")
```

#### CapEx

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "capex", params$ticker, "Capital Expenditures (TTM)")
```

#### Dividends

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "dividends", params$ticker, "Dividends (TTM)")
```

#### Buybacks

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "buybacks", params$ticker, "Share Buybacks (TTM)")
```

*Positive = share repurchases (capital returned to shareholders). Negative = share issuance (dilution).*

#### Total Capital Returned

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "total_capital_returned", params$ticker, "Total Capital Returned (TTM)")
```

*Dividends + Share Buybacks*

#### Cash from Investing

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "cashflow_investing", params$ticker, "Cash from Investing (TTM)")
```

#### Cash from Financing

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "cashflow_financing", params$ticker, "Cash from Financing (TTM)")
```

### Balance Sheet {.tabset}

#### Total Assets

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "total_assets", params$ticker, "Total Assets")
```

#### Current Assets

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "current_assets", params$ticker, "Current Assets")
```

#### Non-Current Assets

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "non_current_assets", params$ticker, "Non-Current Assets")
```

#### Cash

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "cash", params$ticker, "Cash & Short-Term Investments")
```

#### Inventory

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "inventory", params$ticker, "Inventory")
```

#### Receivables

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "receivables", params$ticker, "Receivables")
```

#### PP&E

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "ppe", params$ticker, "Property, Plant & Equipment")
```

#### Intangibles

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "intangibles", params$ticker, "Intangible Assets")
```

#### Goodwill

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "goodwill", params$ticker, "Goodwill")
```

#### Total Liabilities

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "total_liabilities", params$ticker, "Total Liabilities")
```

#### Current Liabilities

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "current_liabilities", params$ticker, "Current Liabilities")
```

#### Non-Current Liabilities

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "non_current_liabilities", params$ticker, "Non-Current Liabilities")
```

#### Total Debt

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "total_debt", params$ticker, "Total Debt")
```

#### Long-Term Debt

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "long_term_debt", params$ticker, "Long-Term Debt")
```

#### Short-Term Debt

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "short_term_debt", params$ticker, "Short-Term Debt")
```

#### Shareholder Equity

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "shareholder_equity", params$ticker, "Shareholder Equity")
```

#### Retained Earnings

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "retained_earnings", params$ticker, "Retained Earnings")
```

#### Shares Outstanding

```{r, fig.width=10, fig.height=6}
safe_bar_plot(params$data, "shares_outstanding", params$ticker, "Shares Outstanding")
```

### KPIs {.tabset}

#### Margins

```{r kpi-margins, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = c("gross_margin", "operating_margin", "net_margin"),
    labels = c("Gross Margin", "Operating Margin", "Net Margin"),
    colors = c("steelblue", "darkgreen", "navy"),
    y_format = "percent",
    y_label = "Margin",
    ticker = params$ticker,
    title_suffix = "Profit Margins"
  )
}
```

#### ROIC

```{r kpi-roic, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "roic",
    labels = "ROIC",
    colors = "navy",
    y_format = "percent",
    y_label = "NOPAT / IC",
    ticker = params$ticker,
    title_suffix = "ROIC"
  )
}
```

#### GROIC

```{r kpi-groic, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "groic",
    labels = "GROIC",
    colors = "steelblue",
    y_format = "percent",
    y_label = "Gross Profit / IC",
    ticker = params$ticker,
    title_suffix = "GROIC"
  )
}
```

#### ROE

```{r kpi-roe, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "roe",
    labels = "ROE",
    colors = "darkgreen",
    y_format = "percent",
    y_label = "Net Income / Equity",
    ticker = params$ticker,
    title_suffix = "ROE"
  )
}
```

#### FCF Conversion

```{r kpi-fcf-conversion, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "fcf_conversion",
    labels = "FCF Conversion",
    colors = "steelblue",
    y_format = "percent",
    y_label = "FCF / NOPAT",
    ticker = params$ticker,
    title_suffix = "FCF Conversion"
  )
}
```

#### Cost of Debt

```{r kpi-cost-of-debt, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "cost_of_debt",
    labels = "Cost of Debt",
    colors = "steelblue",
    y_format = "percent",
    y_label = "Interest / Avg Debt",
    ticker = params$ticker,
    title_suffix = "Cost of Debt"
  )
}
```

#### Interest Coverage

```{r kpi-coverage, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "interest_coverage",
    labels = "Interest Coverage",
    colors = "steelblue",
    y_format = "turns",
    y_label = "EBIT / Interest",
    ticker = params$ticker,
    title_suffix = "Interest Coverage"
  )
}
```

#### Leverage

```{r kpi-leverage, fig.width=10, fig.height=6}
if (!is.null(params$kpi_data) && nrow(params$kpi_data) > 0) {
  plot_financial_ratio(
    data = params$kpi_data,
    ratio_cols = "debt_to_ebitda",
    labels = "Debt / EBITDA",
    colors = "steelblue",
    y_format = "turns",
    y_label = "Debt / EBITDA",
    ticker = params$ticker,
    title_suffix = "Leverage"
  )
}
```

## Per-Share Growth {.tabset}

### Revenue

```{r per-share-revenue, fig.width=10, fig.height=6}
if (!is.null(params$per_share_revenue) && nrow(params$per_share_revenue) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_revenue,
    ticker = params$ticker,
    metric_name = "Revenue"
  )
}
```

### Gross Profit

```{r per-share-gross-profit, fig.width=10, fig.height=6}
if (!is.null(params$per_share_gross_profit) && nrow(params$per_share_gross_profit) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_gross_profit,
    ticker = params$ticker,
    metric_name = "Gross Profit"
  )
}
```

### EBIT

```{r per-share-ebit, fig.width=10, fig.height=6}
if (!is.null(params$per_share_ebit) && nrow(params$per_share_ebit) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_ebit,
    ticker = params$ticker,
    metric_name = "EBIT"
  )
}
```

### EBITDA

```{r per-share-ebitda, fig.width=10, fig.height=6}
if (!is.null(params$per_share_ebitda) && nrow(params$per_share_ebitda) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_ebitda,
    ticker = params$ticker,
    metric_name = "EBITDA"
  )
}
```

### NOPAT

```{r per-share-nopat, fig.width=10, fig.height=6}
if (!is.null(params$per_share_nopat) && nrow(params$per_share_nopat) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_nopat,
    ticker = params$ticker,
    metric_name = "NOPAT"
  )
}
```

### FCF

```{r per-share-fcf, fig.width=10, fig.height=6}
if (!is.null(params$per_share_fcf) && nrow(params$per_share_fcf) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_fcf,
    ticker = params$ticker,
    metric_name = "FCF"
  )
}
```

### Operating Cash Flow

```{r per-share-cfo, fig.width=10, fig.height=6}
if (!is.null(params$per_share_cfo) && nrow(params$per_share_cfo) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_cfo,
    ticker = params$ticker,
    metric_name = "Operating Cash Flow"
  )
}
```

### Book Value

```{r per-share-bv, fig.width=10, fig.height=6}
if (!is.null(params$per_share_bv) && nrow(params$per_share_bv) > 0) {
  plot_share_count_decomposition(
    data = params$per_share_bv,
    ticker = params$ticker,
    metric_name = "Book Value"
  )
}
```

## Return Decomposition {.tabset}

### ROIC

```{r roic-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$roic_data) && nrow(params$roic_data) > 0) {
  plot_dupont_over_time(
    data = params$roic_data,
    ticker = params$ticker,
    return_label = params$roic_labels$return_label,
    effect_label = params$roic_labels$effect_label,
    numerator_name = "NOPAT",
    denominator_name = "Invested Capital",
    multiplier_label = params$roic_labels$multiplier_label,
    title_suffix = params$roic_labels$title_suffix,
    roa_label = params$roic_labels$roa_label
  )
}
```

### ROE

```{r roe-decomposition, fig.width=10, fig.height=6}
if (!is.null(params$roe_data) && nrow(params$roe_data) > 0) {
  plot_dupont_over_time(
    data = params$roe_data,
    ticker = params$ticker,
    return_label = params$roe_labels$return_label,
    effect_label = params$roe_labels$effect_label,
    numerator_name = "Net Income",
    denominator_name = "Equity",
    multiplier_label = params$roe_labels$multiplier_label,
    title_suffix = params$roe_labels$title_suffix,
    roa_label = params$roe_labels$roa_label
  )
}
```
